---
title: "Skew Post Chapter"
output: html_notebook
---

```{r setup}
library(tidyquant)
library(tidyverse)
library(timetk)
library(tibbletime)
```

Idea, take SP500, sample randomly, find highest lowest skew. 
Or, take all of SP500, take top 5, bottom 5. 
Group by sector, high low skew per sector.

App idea, choose a portfolio, see how distributed across the globe, run diagnostics, run montecarlo


```{r, warning=FALSE, message=FALSE}
symbols <- c("SPY","EFA", "IJS", "EEM","AGG")
```

XTS World

```{r}
prices <- 
  getSymbols(symbols, src = 'yahoo', from = "2013-01-01", 
             auto.assign = TRUE, warnings = FALSE) %>% 
  map(~Ad(get(.))) %>%
  reduce(merge) %>% 
  `colnames<-`(symbols)

prices_monthly <- to.monthly(prices, indexAt = "last", OHLC = FALSE)

asset_returns_xts <- na.omit(Return.calculate(prices_monthly, method = "log"))

w <- c(0.25, 0.25, 0.20, 0.20, 0.10)

portfolio_returns_xts <- 
  Return.portfolio(asset_returns_xts, weights = w, rebalance_on = "months") %>%
  `colnames<-`("returns") 

skew_xts <-  skewness(portfolio_returns_xts$returns)

```

Tidyverse

```{r}
asset_returns_tidyverse <-  
  prices %>% 
  to.monthly(indexAt = "last", OHLC = FALSE) %>% 
  tk_tbl(preserve_index = TRUE, rename_index = "date") %>%
  gather(asset, returns, -date) %>% 
  group_by(asset) %>%  
  mutate(returns = (log(returns) - log(lag(returns)))) %>% 
  na.omit() %>%
  tq_portfolio(assets_col = asset,
               returns_col = returns,
               weights = w,
               col_rename = NULL,
               rebalance_on = "months",
               wealth.index = FALSE) %>%
  rename(returns = portfolio.returns)

skew_tidy <-
  asset_returns_tidyverse %>% 
  summarise(skew = skewness(returns),
            skew_byhand = 
              (sum((returns - mean(returns))^3)/length(returns))/
              ((sum((returns - mean(returns))^2)/length(returns)))^(3/2)) %>% 
  select(skew, skew_byhand)
  
```

Tidyquant

```{r}
asset_returns_tq <- 
  symbols %>% 
  tq_get(get = "stock.prices", from = "2013-01-01") %>% 
  group_by(symbol) %>% 
  na.omit() %>% 
  tq_transmute(adjusted, periodReturn, period = "monthly", col_rename = "returns") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = returns,
               weights = w,
               col_rename = NULL,
               rebalance_on = "months",
               wealth.index = FALSE)

skew_tq <- 
  asset_returns_tq %>% 
  summarise(skew = skewness(portfolio.returns))
```

```{r}
skew_xts
skew_tidy
#skew_tq
```

We have confirmed the results are consistent using XTS and our tidyverse, by-hand, tidyquant method. The result itself, `r skew_xts`, seems a relatively benign negative skew. However, it's hard to grasp what that number is communicating without a visualization. Ironically, I interpret that numerical result as a guide to my visualization, when normally the opposite would be true. 

We've already visualized the returns in a [previous post]() and here they are again: 

```{r}
asset_returns_tidyverse %>% 
ggplot(aes(x = returns)) + 
geom_histogram(alpha = 1, binwidth = .003, fill = "cornflowerblue", color = "cornflowerblue")
```

```{r}
asset_returns_tidyverse %>% 
ggplot(aes(x = returns)) +
  stat_density(geom = "line", alpha = 1, colour = "cornflowerblue") +
  ggtitle("Portfolio Monthly Returns Since 2013") +
  xlab("monthly returns") +
  ylab("distribution")
```

There seems to be one highly negative return (worse than -.08) and several between -.04 and -.08. But this doesn't give me a great sense of whether we need to worry about this portfolio, or pat ourselves on the back for creating a portfolio with low skewness. To do that, it helps to compare this to other portfolios.

Blog Post 2
And a Tidyquant method for testing out variations of our portfolio

```{r message=FALSE, warning=FALSE}

asset_returns_3 <- 
  symbols %>% 
  tq_get(get = "stock.prices", from = "2013-01-01") %>% 
  group_by(symbol) %>% 
  tq_transmute(adjusted, periodReturn, period = "monthly", col_rename = "returns")

mult_weekly_returns <- tq_repeat_df(asset_returns_3, n = 3)

weights_table <-  
            c(0.25, 0.25, 0.20, 0.20, 0.10,
              0.20, 0.20, 0.25, 0.25, 0.10,
              0.20, 0.20, 0.20, 0.20, 0.20)


weights_table <- tibble(symbols) %>%
    tq_repeat_df(n = 3) %>%
    bind_cols(tibble(weights)) %>%
    group_by(portfolio)

levels <- c("date", paste("portfolio_", 1:3, sep = ""))

portfolios_3 <- 
  mult_weekly_returns %>%
  tq_portfolio(assets_col = symbol,
               returns_col = returns,
               weights = weights_table,
               col_rename = NULL,
               wealth.index = FALSE) 
%>% 
  spread(portfolio, portfolio.returns) %>% 
  `colnames<-`(levels)

skews <- 
  portfolios_3 %>%
  select(-date) %>%
  gather(portfolio, returns) %>%
  group_by(portfolio) %>%
  na.omit() %>% 
  summarise(skew = skewness(returns),
            skew_byhand = 
              (sum((returns - mean(returns))^3)/length(returns))/
              ((sum((returns - mean(returns))^2)/length(returns)))^(3/2),
            kurt = kurtosis(returns),
            kurt_byhand = 
              ((sum((returns - mean(returns))^4)/length(returns))/
              ((sum((returns - mean(returns))^2)/length(returns))^2)) - 3)

```

```{r}
portfolios_3 %>% 
  ggplot(aes(x = portfolio.returns)) + 
  geom_histogram(alpha = 1, binwidth = .01, fill = "cornflowerblue", 
                 color = "cornflowerblue") +
  ggtitle("Portfolio Monthly Returns Since 2013") +
  xlab("monthly returns") +
  ylab("distribution") + 
  facet_wrap(~portfolio)
```


```{r}
portfolios_3 %>% 
  ggplot(aes(x = portfolio.returns)) + 
  stat_density(geom = "line", alpha = 1, colour = "cornflowerblue") +
  ggtitle("Portfolio Monthly Returns Since 2013") +
  xlab("monthly returns") +
  ylab("distribution") + 
  facet_wrap(~portfolio)
```


Blog Post 3
SP500 by sector